\textbf{Computational Fuzzy Extractors}

### 2013-05-16 trunk/CompFuzzExt.tex
minor fixing

%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.  Random linear codes~(in the Hamming metric) already achieve min-entropy $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.  Do we prefer $n\log Z$?}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.

@@

\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
\label{sec:imp unp sketch}
In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.  A reasonable question to ask is whether a sketch could retain unpredictability of the source.  We begin by defining conditional unpredictability entropy:

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
For a distribution $(W, S)$, we say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a collection of distributions $X_s$ (giving rise to a joint distribution $(X, S)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, S))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
\[
\Pr[\mathcal{I}(Z) = Y ] \leq 2^{-k}
.\]
\end{definition}
We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch} with the security requirement replaced with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(as shown by \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
%\footnote{See~\cite{barak-computational} for the definition of reconstruction extractor.}.   show that unpredictability entropy can be e.
%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
%\label{lem:unp extraction} 
%\bnote{We can't use the letter $C$ its taken for a distribution of codewords.}\bnote{We also $D$ as a distinguisher elsewhere.}
%Let $W$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(W|S)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(W, U_d), S), U_m\times U_d\times S)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
%\end{lemma}
%Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
Unfortunately, the unpredictability entropy conditioned on the sketch must decrease as $t$ increases.  
%An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.  %That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.  
The formal statement is below:
\bnote{Should we list the stronger statement in the appendix or keep this for clarity?}
\begin{theorem}
\label{thm:imp of unp entropy}
Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an unpredictability-entropy \\$(Z^n, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
\end{theorem}
This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  In \secref{sec:proof of imp unp entropy}, we prove a stronger theorem for larger class of metric spaces and for a relaxed notion of unpredictability entropy~(similar to the relaxed notion of HILL entropy in \defref{def:relaxed hill}).%Our bound is a result of the Hamming bound for the space.

@@

\begin{theorem}
Let $W$ be a distribution over a metric space $(\mathcal{M}, \dis)$ that is $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable.  Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is fixed~(this quantity is denoted by $B_t(\cdot)$).  Let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
\end{theorem}
\begin{proof}
Let $\mathcal{M}, \dis$ be a $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable metric space~(by procedures $\sample$ and $\neigh$ respectively).  
Let $W$ be a distribution over $\mathcal{M}$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$.  Let $X, Y$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.  It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq 2^{\tilde{m}}$ where $\tilde{m} = \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.

>>>>

%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.  The code-offset sketch instantiated with a random linear code~(in the Hamming metric)  achieve min-entropys $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.  Do we prefer $n\log Z$?} \lnote{I think your change is fine}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.

@@

\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
\label{sec:imp unp sketch}
In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.  However, HILL entropy is a strong notion.  In this section, we therefore ask whether it is useful to consider a sketch that satisfies a minimal requirement: the value of the input is computationally hard to guess given the sketch.  We begin by recalling the definition of conditional unpredictability entropy, which captures the notion of ``hard to guess'' (we relax it similar to the way conditional HILL entropy was relaxed in the previous section).

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
Let  $(W, S)$ be a pair of random variables. We say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a pair of distributions $(X, Y)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
\[
\Pr[\mathcal{I}(Y) = X ] \leq 2^{-k}
.\]
\end{definition}

We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-
hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
Note this notion is quite natural: combining such a secure sketch via  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor 
\emph{reconstructive}~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).

Unfortunately, the conditional unpredictability entropy $\tilde{m}$ must decrease as $t$ increases, as the following theorem states.  (The proof of the theorem, generalized to more metric spaces, is in \secref{sec:proof of imp unp entropy}.)

\begin{theorem}
\label{thm:imp of unp entropy}
Let $Z$ be an alphabet $(\sketch, \rec)$ be an unpredictability-entropy $(Z^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
\end{theorem}
In particular, if the input is uniform, the entropy loss is about $\log |B_t(\cdot)|$.  Essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the code-offset construction\lnote{cite here, and is it the randomized construction or the deterministic one that we should use here?} applied to the best possible codes (e.g., random codes\lnote{cite performance of codes?}).  Thus, unpredictability-entropy secure sketches cannot improve on the best possible information-theoretic entropy loss (at least for uniform inputs).  However, because the best possible codes may not have efficient decoding, it is conceivable that unpredictability entropy secure sketch could achieve lower entropy loss than is possible with efficient information-theoretic sketches.

This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  \lnote{I find the previous three sentences more confusing than helpful; do we really need them?  should we reword or remove?} %Our bound is a result of the Hamming bound for the space.

@@

\begin{theorem}
Let $W$ be a distribution over a metric space $(\mathcal{M}, \dis)$ that is $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable.  Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is fixed~(this quantity is denoted by $B_t(\cdot)$).  Let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
\end{theorem}
\begin{proof}
Let $\mathcal{M}, \dis$ be a $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable metric space~(by procedures $\sample$ and $\neigh$ respectively).  
Let $W$ be a distribution over $\mathcal{M}$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$.  Let $X, Y$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.  It suffices to show that $\exists \ \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq 2^{\tilde{m}}$ where $\tilde{m} = \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
